Stat 400 Project

### 2021-11-29 Stat 400 proj.Rmd
tried making a coord checker

@@

    if(i == 1){
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(initial_data, change)
    updated_state <- cbind(updated_positions, initial_data[,3])
    new_status <- infection_status(updated_state, 2)
    end_day[[i]] <- cbind(updated_positions, new_status)
    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(end_day[[i-1]], change)
    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
    new_status <- infection_status(updated_state, 1/5)
    end_day[[i]] <- cbind(updated_positions, new_status)

>>>>

coord_checker <- function(updated, x_dim, y_dim){
  num_bads <- 0
  for(i in 1:nrow(updated)){
    if(as.numeric(updated[i, 'x']) > x_dim | as.numeric(updated[i, 'y']) > y_dim){
      new_step <- get_step_length(updated[i,], x_dim, y_dim)
      new_direction <- get_step_direction(new_step)
      new_change <- get_delts(new_step, new_direction)
      # new_df[i,1] <- as.numeric(og_df[i,'x']) + new_change[,'delta_x']
      # new_df[i,2] <- as.numeric(og_df[i,'y']) + new_change[,'delta_y']
      updated[i,] <- update_coords(updated[i,], new_change)
      num_bads <- num_bads + 1
    }
  }
  if(num_bads==0){
    return(updated)
  }
}

@@

    if(i == 1){
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(initial_data, change, x_dim, y_dim)
    updated_state <- cbind(updated_positions, initial_data[,3])
    new_status <- infection_status(updated_state, 2)
    end_day[[i]] <- cbind(updated_positions, new_status)
    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(end_day[[i-1]], change, x_dim, y_dim)
    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
    new_status <- infection_status(updated_state, 1/5)
    end_day[[i]] <- cbind(updated_positions, new_status)
